Outstanding Title

### 2017-02-21 writing/JSSDraft/JSSDraft.Rmd
Write epi intro

  Developing the code to simulate environmental time series for these types of studies can be time consuming, and simulation methods have varied across previous simulation studies, complicating the comparison of results across different studies. Here, we present an R package that automates simulation of environmental time series for such simulations, offering both sensible defaults for each stage of the simulation process and also the option to customize any of the simulation steps while using defaults for any steps that do not require customization. This packge can be used to aid simulation studies to explore environmental epidemiology models relating acute health outcomes and daily environmental exposures; it can also be used to estimate the power of studies when planning or proposing future research.
keywords:
  # at least one keyword must be supplied
  formatted: [R, environmental epidemiology, simulation studies, power analysis, air pollution]
  plain:     [R, environmental epidemiology, simulation studies, power analysis, air pollution]
preamble: >
  \usepackage{amsmath}
output:
  rticles::jss_article:
    citation_package: natbib
bibliography: mybibfile.bib
---

>>>>

  Developing the code to simulate environmental time series for these types of studies can be time consuming, and simulation methods have varied across previous simulation studies, complicating the comparison of results across different studies. Here, we present an R package that automates simulation of environmental time series for such simulations, offering both sensible defaults for each stage of the simulation process and also the option to customize any of the simulation steps while using defaults for any steps that do not require customization. This package can be used to aid simulation studies to explore environmental epidemiology models relating acute health outcomes and daily environmental exposures; it can also be used to estimate the power of studies when planning or proposing future research.
keywords:
  # at least one keyword must be supplied
  formatted: [R, environmental epidemiology, simulation studies, power analysis, air pollution]
  plain:     [R, environmental epidemiology, simulation studies, power analysis, air pollution]
preamble: >
  \usepackage{amsmath}
output:
  rticles::jss_article:
    citation_package: natbib
bibliography: mybibfile.bib
---
